### 2018-05-30 msc_diploma_cubesat_galgoczi.tex
txt

The detector and the satellite was radiated with a parallel $\gamma$-rays. The energy spectrum of these particles was chosen to be the same as GRB 9900123. In order to understand  how the satellite would absorb the $\gamma$-rays several simulations were carried out by chaning the incident angle of the beam around the longitudinal axis of the satellite.

@@

Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet least understood astrophysical objects. They have been studied for more than fourty years as one of the most extreme explosive events in the Universe. Their origin is still not yet fully understood. GRBs were discovered in 1967–73 by military satellites. The scientific community only got to know their existance in the early seventies \cite{grb5}. A GRB event is brighter than any other object in the sky during its appearance that can last from a millisecond to minutes. Every day a new GRB is observed by the satellites investigating them. The main part of the energy spectrum of these events in the keV to the MeV ranges.

@@

One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jets \cite{grb10}. For most of the observed GRBs the prompt $\gamma$-ray emission was followed by a longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}. This is due to the propagation of a relativistic shockwave through the medium that surrounds the burst. Observations proved that GRBs are at cosmological distances \cite{grb12}. The farthest GRB observed was at a distance of z=9.4. The avarge short GRBs lie at a distance of z=0.5. The long GRBs are even farther away, on avarage at z=2. The energy that is released in such an event is tremendous, about 10 erg. Long GRBs have been linked to the brightest regions of galaxies those contain the the most massive stars \cite{grb14}. %The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/GRB_BATSE_12lightcurves.png}
\caption{The light curves of 12 gamma-ray bursts observed by BATSE. The diversity of the curves is extraordinary. Events with a length from millisecond to a second exist either with smooth or highly variable curves.}
\end{figure}

On the contrary, short GRBs are thought to originate in old populations. The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves of such events. This was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}. The electromagnetic counterpart of this gravitational wave event was detected as a short GRB by the Fermi/Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}. Short GRBs emit electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.

@@

Despite the fact that GRBs have been studied for more than fourty years a lot of questions are still not understood about their physics\cite{grb19}. In the following the main open questions are listed:

@@

This subsection provides an overview of the existing missions that are aimed to detect GRBs. Field of view (FOV) and localization accuracy are chosen to compare them with the Camelot CubeSat. The proposed design of the Camelot satellite has the advantage of a large field of view and a high localization accuray. The main idea is that each CubeSat will detect GRBs at the same time. By measuring the time difference between the triggering of each satellite, the GRB soure can be triangularized. By using more satellites, the field of view becomes full-sky and localization accuracy increases.

The planed localization accuracy is more precise than any other existing GRB mission, that might reach $\sim$10'. While providing the highest lcoalization accuracy, the field of view would also be the highest, even larger than the field of view of the INTEGRAL/SPI-ACS and Fermi.

The size and mass of the Camelot CubeSat is less than 1\% of the Fermi telescope. Therefore from a fraction of the cost several satellites could be built and deployed in orbit. Having several satellites also provide a high redundance.

@@

\begin{itemize}
\item Fermi 7 \cite{grb28} was launched in 2008 and its main instruments are the Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
\item Neil Gehrels Swift Observatory (Swift) 8 \cite{grb31} was launched in 2005 with its main instruments, those are the Burst Alert Telescope (BAT),  the X-ray Telescope (XRT), and the UV/Optical Telescope (UVOT).
\item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) 9 \cite{grb32} was launched in 2002. The most succesfull instruments on board include are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the "Imager on Board the Integral Satellite (IBIS)" detector.
\item Astro-Rivelatore Gamma a Immagini Leggero (AGILE) 11 \cite{grb34} was launched in 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
\item CALorimetric Electron Telescope (CALET) 12 \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
\item Monitor of All-sky X-ray Image (MAXI) 13 \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. This instrument is placed on ISS.
\item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of $\gamma$-rayGRB polarization.
\item Lomonosov 15 /BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
\item The Hard X-ray Modulation Telescope (Insight-HXMT) 16 \cite{grb39} was launched in 2017. It has the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
\item ASTROSAT 17 \cite{grb40} was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
\item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) 18 \cite{grb41}, was launched in 2002. It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
\end{itemize}

@@

The CAMELOT satellite platform is being developed by C3S LLC, in Budapest. There would most likely be four scintillators on the CAMELOT satellite. On two neighbouring sides of the satellite have two scintillators each. The scintillators will have a case either from aluminium or carbon fibre.

@@

In the case of our satellite, the detection of $\gamma$ photons from GRBs will be carried out by a Caesium Iodide scintillator doped with Tellurium. This is the most popular alkali halide scintillation crystal apart from NaI(Tl). The $\gamma$ photons create scintillation, thus thousands of optical photons in the scintillator. These photons will be detected by Silicon Photomultiplier device called Multi Pixel Photon Counter, MPPC for short. This if by far the best and most compact solution as the size of cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$. The first tests were carried out by a single MPPC readout, which was followed by a design with two MPPCs to maximize the light yield and minimalize the noise. The size of the Hamamatsu MPPC is 6x6 mm$^{2}$. The scintillators will be placed onto the surface of the satellite as can be seen in fig. \ref{fig:scints}. While fig. \ref{fig:schem} shows the experimental setup used for the tests.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{Side extensions including the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
\label{fig:scints}
\end{figure}

The large area and small thickness of the scintillator makes it challenging for the read out as optical photons have to be reflected several times to reach the MPPC. Two factors play role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator. The length of the self absorption is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig. \ref{fig:refl}. The idea that we came up is using two MPPC-s with coincidence. This results in a smaller leakage current (noise) as the noise has a poissonian statistic. Therefore the noise is "random" and the chance of a trigger from both of the MPPC has a very low chance. The other advantage is the incread photon yield due to the double of the photon collection area. The difference between one and two channel readout can be seen in fig. \ref{fig:spectra}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\label{fig:spectras_meas}
\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
\label{fig:spectra}
\end{figure}

@@

The most used software in particle physics are MCNPX, FLUKA and Geant4. For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is most propably is the most convinient in this software.

Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using the Monte Carlo method. It has been developed at CERN for more than three decades by dozens of physicst and programmers. The cross sections for all interactions between matter and particles are included in this software. It is an object orianted programming platform in C++. Its development, maintenance and user support are taken care by the international Geant4 Collaboration. Areas in science that has used Geant4 are vary widely from the design of complex medical machines to accelerator, nuclear physics, high energy physics and space applications. Several thousand people use it all around the globe.

@@

In order to understand and charaterize the behaviour of the large-area CsI(Tl) scintillator detector and the MPPC readout; an experimental setup was built in Hiroshima, Japan. The experimental setup provided vital information for the simulation, mostly for the position dependence of the light yield. Different $\gamma$ source were used, mostly an $^{241}$Am source.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right \cite{kento}}
 \end{figure}

@@

The CsI(Tl) scintillator used is produced by AmCrys \cite{scinti}. The dimension of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the satellite. The spectra of the optical photons produced in the scintillation process can be seen in fig. \ref{fig:scint_yield}. An aluminium case of 2mm is used, the same as planned for the mission in space. The time constant for the scintillation of the detector was 200 ns.

@@

The response of the MPPC detector used depends on temperature. Therefore the experimental setup was placed in a thermostatically controlled chamber (ESPEC LU-113) keeping the temperature at 25$^{\circ}$. Two setups were investigated. The first one with a single MPPC readout placed in the middle of one side of the scintillator. In the other case two MPPCs were utilized symmetrically placed on one side of the detector.

@@

\begin{figure}
\begin{center}
\includegraphics[width=80.0mm]{images/1channelelectronics.png}
\caption{The schematic design of the readout of the MPPC for the 1 channel configuration \cite{kento}}
\label{fig:el1ch}
\end{center}
\end{figure}

@@

The $\gamma$ source that was used to test the experimental setup was choosen to be an $^{241}Am$. The reason for this is that the peak of energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV. The activity of the source at the time of the experiment was 471 kBq. The source was collimated to a beam that hit the surface of the scintillator on a circle with a radius of 10 mm. The distance of the source from the scintillator was 13.5 mm.

@@

The direction of GRBs is isotropic in the sky as they are extragalactic objects. As the position of the scintillators is not decided yet it is important to understand which configuration would be the best in order to detect as many GRBs as possible. Therefore it is vital to understand how the material of the satellite itself absorbs $\gamma$-rays. The satellite consists of several modules with specific shapes and material contents. Therefore building up the whole geometry and material composition was not possible in Geant4, thus the model of the satellite had to be  imported into Geant4.

@@

The material composition of the satellite can not be exported to Geant4 from CAD files directly. Therefore an avarage material composition was calculated for all the modules. In table $\ref{table:materials}$ the material composition of the 7 modules are listed. These materials, mostly alloys consist of several elements. The Geant4 cross section database is built up only for elements. Therefore these materials had to be broken down to elements.

@@

In fig. \ref{fig:sat_rad} the simulation of the satellite and the two channel read out setup can be seen. 100 $\gamma$ particles were used to shoot the satellite with a beam parallel to the plane of the scintillator. A scattered $\gamma$ particle can be seen scattered into the scintillator and being detected.

@@

The measured spectra of the scintillation light created by $\gamma$-rays (fig. \ref{fig:spectras_meas}) has a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source. There is an additional peak with an amplitude of roughly 20 \% of the main peak. The physical process that is behind this is the X-ray fluoresence. By default this process is not included in Geant4 simulations, thus I had to turn it on. A histogram with and without x-ray fluorescence can be seen in fig. \ref{fig:fluo}

@@

A lead sheet was drilled with nine holes to collimate the $\gamma$ source to certain parts of the scintillator. These measurements were carried out by Kento Torigoe at the University of Hiroshima. This configuration with a lead sheet was built up in Geant4 (fig. \ref{fig:this_set} and 3.6 million $\gamma$s were simulated at each position.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\caption{The number of detections from the 10,000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
\label{fig:diffpos}
\end{center}
\end{figure}

@@

In fig. $\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator with a perpendicular direction and when they hit the satellite from behind. The difference between these two scenarious is that $\gamma$s had to travel through the material of the satellite in the second case. About 60 \% of gammas are lost do the absorption of the satellite.

@@

A Geant4 Monte-Carlo based simulation was developed in order to understand how the CAMELOT CubeSat would detect $\gamma$-rays originating from short GRBs. The effect of solar and cosmic electrons on the satellite was also investigated with the simulation.

As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the particle detector of the satellite -- was implemented in Geant4. The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs in the simulation with experimental data. After the calibration, the results of the simulation was capable of predicting the signal that would be measured in space.

Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a given avarage material composition-- was exported to Geant4. The scintillator and its read out was placed on the side of the satellite.

Thirdly, the $\gamma$ absorption of the satellite was invastigated. Parallel $\gamma$-rays with the energy distribution of GRB 9900123 (fig. \ref{fig:grb_band}) was simulated. 36 positions were investigated by varying the incident angle of the $\gamma$s around the major axis of the satellite.

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km. The satellite was radiated by these particles in Geant4 in the same way that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined, which is about one order of magnitude lower than the signal of a GRB. The induced signal of electrons needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.

>>>>

The detector and the satellite was radiated with a parallel beam of $\gamma$-rays. The energy spectrum of these particles was chosen to be the same as GRB 9900123. In order to understand  how the satellite would absorb the $\gamma$-rays several simulations were carried out by changing the incident angle of the beam around the longitudinal axis of the satellite.

@@

Gamma-ray bursts (GRBs) \cite{grb1,grb2,grb3,grb4} are one of the most invesitaged and yet least understood astrophysical objects. They have been studied for more than fourty years as one of the most extreme explosive events in the Universe. Their origin is still not fully understood. GRBs were discovered in 1967–73 by the VELA military satellites. The scientific community only got to know about their existance in the early seventies \cite{grb5}. A GRB event is brighter than any other object in the sky during its appearance that can last from a millisecond to minutes. Every day a new GRB is observed by the satellites investigating them. The main part of the energy spectrum of these events is in the keV to the few MeV range.

@@

One of the most accepted theories describe GRBs as collisions of highly relativistic outflow of the accelerated jets \cite{grb10}. For most of the observed GRBs the prompt $\gamma$-ray emission was followed by a longer-lasting afterglow in soft X-ray, optical or radio waves \cite{grb11}. This is due to the propagation of a relativistic shockwave through the medium that surrounds the burst. Observations proved that GRBs are at cosmological distances \cite{grb12}. The farthest GRB observed was at a distance of z=9.4. The avarge short GRBs lie at a distance of z=0.5. The long GRBs are even farther away, on avarage at z=2. The energy that is released in such an event is tremendous, about 10 erg. Long GRBs have been linked to the brightest regions of galaxies those that contain the most massive stars \cite{grb14}. %The relativistic outflow of LGRBs has a bulk Lorentz factor of $\Gamma\sim$300 [5]. The afterglow observations indicate that a geometrical beaming of the LGRBs radiation has an opening angle of $\sim$5 \cite{grb15}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/GRB_BATSE_12lightcurves.png}
\caption{The light curves of 12 gamma-ray bursts observed by BATSE. The diversity of the curves is extraordinary. Events with a length from millisecond to tens of seconds exist either with smooth or highly variable light curves.}
\end{figure}

On the contrary, short GRBs are thought to originate in old populations. The theory that they originate from the merging of two neutron stars has been recently confirmed by detecting the gravitational waves from such an event. GW170818 was detected by the LIGO/Virgo collaboration in 2017 \cite{gravwave}. The electromagnetic counterpart of this gravitational wave event was detected as a short GRB by the Fermi/Gamma-ray Burst Monitor (GBM) and INTEGRAL instruments followed by the observation of the GRB’s afterglow and its host galaxy \cite{grb17}. Kilonovae producing infrared electromagnetic radiation due to the radioactive decay of heavy r-process nuclei that are produced and ejected almost isotropically during the merger process \cite{grb18}.

@@

Despite the fact that GRBs have been studied for more than fourty years many questions are still not understood about their physics\cite{grb19}. In the following the main open questions are listed:

@@

This subsection provides an overview of the existing missions that are aimed to detect GRBs. Field of view (FOV) and localization accuracy are chosen to compare them with the CAMELOT mission. The proposed design of the CAMELOT satellites has the advantage of a large field of view and a high localization accuray. The main idea is that each CubeSat will detect GRBs at the same time. By measuring the time difference between the triggering of each satellite, the GRB soure can be localized by triangulation. By using more than nine satellites, the constellation achieves all sky coverage and localization accuracy.

The planed localization accuracy might reach $\sim$10'. While providing a good localization accuracy, the field of view would be even larger than  that of the INTEGRAL/SPI-ACS and Fermi.

The size and mass of the Camelot CubeSat is less than 1\% of the Fermi telescope. Therefore from a fraction of the cost several satellites could be built and deployed in orbit. Having several satellites also provides redundance.

@@

\begin{itemize}
\item Fermi \cite{grb28} was launched in 2008 and its main instruments are the Gamma-ray Burst Monitor and the Large Area Telescope (LAT). 
\item Neil Gehrels Swift Observatory (Swift) \cite{grb31} was launched in 2005 with its main instruments, those are the Burst Alert Telescope (BAT),  the X-ray Telescope (XRT), and the UV/Optical Telescope (UVOT).
\item INTErnational Gamma-Ray Astrophysics Laboratory (INTEGRAL) \cite{grb32} was launched in 2002. The most succesfull instruments on board include are the Anti-Coincidence Shield of the SPectrometer of INTEGRAL (SPI-ACS) and the Integral Soft Gamma-Ray Imager (ISGRI) detector layer of the "Imager on Board the Integral Satellite (IBIS)" detector.
\item Astro-Rivelatore Gamma a Immagini Leggero (AGILE)  \cite{grb34} was launched in 2007 and its Hard X-ray Imaging Detector (Super-AGILE) detected several GRBs.
\item CALorimetric Electron Telescope (CALET)  \cite{grb35} / Gamma-Ray Burst Monitor (CGBM), was launched in 2015 and it is placed on the International Space Station (ISS).
\item Monitor of All-sky X-ray Image (MAXI) \cite{grb36}, started nominal observation in 2009. Its instrument Gas Slit Camera (GSC) detects GRBs. This instrument is placed on ISS.
\item Gamma-ray Burst Polarimeter POLAR 14 \cite{grb37}, was launched in 2016 and is dedicated to the measurement of $\gamma$-rayGRB polarization.
\item Lomonosov/BDRG \cite{grb38}, was launched in 2016. The BDRG instrument on board detected several GRBs.
\item The Hard X-ray Modulation Telescope (Insight-HXMT) \cite{grb39} was launched in 2017. It has the high energy X-ray telescope (HE), the medium energy X-ray telescope, and the low energy X-ray telescope.
\item ASTROSAT \cite{grb40} was launched in 2015 and its Cadmium Zinc Telluride Imager (CZTI) has already detected many GRBs.
\item Reuven Ramaty High Energy Solar Spectroscopic Imager (RHESSI) \cite{grb41}, was launched in 2002. It is designed to study hard x-ray and gamma-ray emission from solar flares, however it is also efficient instrument to detect non-solar gamma-ray events like GRBs.
\end{itemize}

@@

The CAMELOT satellite platform is being developed by C3S LLC, in Budapest. There would most likely be four scintillators on the CAMELOT satellite, on two neighbouring sides of the satellite, two scintillators each. The scintillators will have a case either from aluminium or carbon fibre.

@@

In the case of our satellite, the detection of $\gamma$ photons from GRBs will be carried out by a Caesium Iodide scintillator doped with Tellurium. This is the most popular alkali halide scintillation crystal apart from NaI(Tl). The $\gamma$ photons create scintillation, thus thousands of optical photons in the scintillator. These photons will be detected by Silicon Photomultiplier device called Multi Pixel Photon Counter, MPPC for short. This is by far the best and most compact solution as the size of cubesat standard is limited to be $\sim$300x75x5 mm$^{3}$. The first tests were carried out by a single MPPC readout, which was followed by a design with two MPPCs to maximize the light yield and minimalize the noise. The size of the Hamamatsu MPPC is 6x6 mm$^{2}$. The scintillators will be placed onto the surface of the satellite as can be seen in fig. \ref{fig:scints}. While fig. \ref{fig:schem} shows the experimental setup used for the tests.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{Side extensions including the CAMELOT satellite (left, based on QB50 system requirements and recommendations) where scintillators are placed and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
\label{fig:scints}
\end{figure}

The large area and small thickness of the scintillator makes it challenging for the read out as optical photons have to be reflected several times to reach the MPPC. Two factors play a role here, the self absorption of the reflectivity of the tape that is used to cover the scintillator. The length of the self absorption is in the order of a meter and the reflectivity of the ESR tape, which is above 99 \% can be seen in fig. \ref{fig:refl}. The idea that we came up is using two MPPC-s with coincidence. This results in a smaller leakage current (noise) as the noise has a poissonian statistic. Therefore the noise is "random" and a trigger from both of the MPPC is unlikely. The other advantage is the increased photon yield due to the double of the photon collection area. The difference between one and two channel readout can be seen in fig. \ref{fig:spectras_meas}.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
\label{fig:spectras_meas}
\end{figure}

@@

The most used software in particle physics are MCNPX, FLUKA and Geant4. For this thesis Geant4 was chosen as it is the best for simulation of several types of particles at the same time and building up the geometry of detectors is propably the most convinient in this software.

Geant4 \cite{geant1, geant2, geant3} (for GEometry ANd Tracking) is a platform for "the simulation of the passage of particles through matter," using the Monte Carlo method. It has been developed at CERN for more than three decades by dozens of physicst and programmers. The cross sections for all interactions between matter and particles are included in this software. It is an object orianted programming platform in C++. Its development, maintenance and user support are taken care of by the international Geant4 Collaboration. Areas in science that have used Geant4 vary widely from the design of complex medical machines to accelerator, nuclear physics, high energy physics and space applications. Several thousands of people use it all around the world.

@@

In order to understand and charaterize the behaviour of the large-area CsI(Tl) scintillator detector and the MPPC readout; an experimental setup was built in Hiroshima, Japan. The experimental setup provided vital information for the simulation, mostly for the position dependence of the light yield. Different $\gamma$ sources were used, mostly an $^{241}$Am source.

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right \cite{kento}}
 \label{fig:schem}
 \end{figure}

@@

The CsI(Tl) scintillator used is produced by AmCrys \cite{scinti}. The dimensions of this detector are 150 mm x 75 mm x 5 mm, the largest possible size that can fit onto the surface of the satellite. The spectra of the optical photons produced in the scintillation process can be seen in fig. \ref{fig:scint_yield}. An aluminium case of 2mm is used, the same as planned for the mission in space. The time constant for the scintillation of the detector was 200 ns.

@@

The response of the MPPC detector used depends on temperature. Therefore the experimental setup was placed in a thermally controlled chamber (ESPEC LU-113) keeping the temperature at 25$^{\circ}$. Two setups were investigated. The first one with a single MPPC readout placed in the middle of one side of the scintillator. In the other case two MPPCs were utilized symmetrically placed on one side of the detector.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=80.0mm]{images/1channelelectronics.png}
\caption{The schematic design of the readout of the MPPC for the 1 channel configuration \cite{kento}}
\label{fig:el1ch}
\end{center}
\end{figure}

@@

The $\gamma$ source that was used to test the experimental setup was choosen to be an $^{241}Am$. The reason for this is that the peak of the energy spectrum of the $\gamma$ photons from GRBs is at 50 keV which is very close to the peak of the $^{241}Am$ that is 59.5 keV. The activity of the source at the time of the experiment was 471 kBq. The source was collimated to a beam that hit the surface of the scintillator on a circle with a radius of 10 mm. The distance of the source from the scintillator was 13.5 mm.

@@

The direction of GRBs is isotropic in the sky as they are extragalactic objects. As the position of the scintillators is not decided yet it is important to understand which configuration would be the best in order to detect as many GRBs as possible. Therefore it is vital to understand how the material of the satellite itself absorbs and scatters $\gamma$-rays. The satellite consists of several modules with specific shapes and material contents. Therefore building up the whole geometry and material composition was not possible in Geant4, thus the model of the satellite had to be  imported into Geant4.

@@

The material composition of the satellite can not be exported to Geant4 from CAD files directly. Therefore an avarage material composition was calculated for all the modules. In table $\ref{table:materials}$ the material compositions of the 7 modules are listed. These materials, mostly alloys, consist of several elements. The Geant4 cross section database is built up only for elements. Therefore these materials had to be broken down to elements.

@@

In fig. \ref{fig:sat_rad} the simulation of the satellite and the two channel read out setup can be seen. 100 $\gamma$ particles were used to shoot the satellite with a beam parallel to the plane of the scintillator. A $\gamma$-ray can be seen scattered into the scintillator and being detected.

@@

The measured spectra of the scintillation light created by $\gamma$-rays (fig. \ref{fig:spectras_meas}) have a main peak that corresponds to the 60 keV $\gamma$s from the $^{241}$Am source. There is an additional peak with an amplitude of roughly 20 \% of the main peak. The physical process that is behind this is X-ray fluoresence. By default this process is not included in Geant4 simulations, thus I had to turn it on. A histogram with and without x-ray fluorescence can be seen in fig. \ref{fig:fluo}.

@@

A lead sheet was drilled with nine holes to collimate the $\gamma$-rays to certain parts of the scintillator. These measurements were carried out by Kento Torigoe at the University of Hiroshima. This configuration with a lead sheet was built up in Geant4 (fig. \ref{fig:this_set} and 3.6 million $\gamma$s were simulated at each position.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\caption{The number of detections from the 10,000 $\gamma$ photons in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
\label{fig:diffpos}
\end{center}
\end{figure}

@@

In fig. $\ref{fig:mac17hits}$ one can see the comparison between the energy spectrum measured when the $\gamma$s hit the scintillator in a perpendicular direction and when they hit the satellite from the side opposite to the scintillator. The difference between these two scenarious is that $\gamma$s had to travel through the material of the satellite in the second case. About 60 \% of gammas are lost due to the absorption in the satellite.

@@

A Geant4 Monte-Carlo based simulation was developed in order to understand how the CAMELOT CubeSat constallation would detect $\gamma$-rays originating from short GRBs. The effect of solar and cosmic electrons on the satellite was also investigated with the simulation.

As the first step, the experimental setup that was used to test the CsI(Tl) scintillator -- the $\gamma$-ray detector of the satellite -- was implemented in Geant4. The optical parameters of the simulation were fine tuned by comparing the light yield of the MPPCs in the simulation with experimental data. After the calibration, the results of the simulation are capable of predicting the signal that would be measured in space.

Secondly, the complex CAD model of the satellite --consisting of 7 modules, each with a given avarage material composition-- was exported to Geant4. The scintillator and its MPPC was placed on the side of the satellite.

Thirdly, the $\gamma$-ray absorption of the satellite was invastigated. Parallel $\gamma$-rays with the energy distribution of the bright GRB 9900123 (fig. \ref{fig:grb_band}) were simulated. 36 positions were investigated by varying the incident angle of the $\gamma$s around the major axis of the satellite.

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at an altitude of 500km in a polar orbit. It is possible that an other orbit will be choosen for the satellite, as the polar parts of the polar orbit have a very high electron flux.

The satellite was radiated by these particles in Geant4 in the same way that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined, which is about one order of magnitude lower than the signal of a GRB. The induced signal of electrons needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.
